---
title: "ML Output Kenya"
author: "Fiona Spooner"
date: "July 23, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(fig.width = 12, fig.height = 9)
```


```{r}
library(here)
library(dplyr)
library(ggplot2)
library(stringr)
library(reshape2)
library(readr)
library(scales)
library(vroom)

```



####Animal vs No Animal

Producing figures to show the total number of images at each site categorised as either Animal or no Animal

```{r,eval = FALSE}

lf<-list.files(here::here("/results_csvs/phase1"), pattern = "*_results.csv", full.names =  TRUE)

filer<-function(file){
  
  file_in<-read.csv(file, header = FALSE)
  file_in$filename<-basename(file)
  return(file_in)  
}

files_out<-lapply(lf, filer)

allp1<-do.call("rbind", files_out)

write.csv(allp1, here::here("results_csvs/phase1/all_sites_seasons.csv"), row.names = FALSE)


```


```{r, echo = FALSE}

allp1<-read.csv(here::here("results_csvs/phase1/all_sites_seasons.csv"), stringsAsFactors = FALSE)
colnames(allp1)<-c("row_no", "IMG_ID","unsure", "Animal", "NoAnimal", "ConfAnim", "ConfNoAnim", "SiteSeason")


```

Formatting the ML output - this is specific to the kenya files data but it just creates a new columns for Site and Season, which are extracted from the file names 

```{r, echo = FALSE}

allp1$Site<-allp1$SiteSeason%>%
              gsub("_november_results.csv", "", .)%>%
              gsub("_october_results.csv", "", .)%>%
              gsub("_november_repaired_results.csv", "", .)%>%
              gsub("_october_repaired_results.csv", "", .)

allp1$Season<-allp1$SiteSeason%>%
              gsub("_results.csv", "", .)%>%
              gsub("_repaired", "", .)%>%
              gsub("mara_north_", "", .)%>%
              gsub("mara_triangle_", "", .)%>%
              gsub("naboisho_", "", .)%>%
              gsub("omc_", "", .)
```


Getting rid of the summary rows at the end of each data sheet and getting rid of the square brackets in the Animal/No Animal columns

```{r}

alldf<-allp1[-which(allp1$Animal != "[0" & allp1$Animal != "[1"),]


alldf$Animal[alldf$Animal == "[0"]<-0
alldf$Animal[alldf$Animal == "[1"]<-1

alldf$ConfAnim<-gsub("\\[","", alldf$ConfAnim)

alldf$IMG_ID_nospl<-alldf$IMG_ID%>%
                      gsub("_0.JPG","", .)%>%
                      gsub("_1.JPG","", .)

```

Merging the split images together by summing the animal column. Anything with a 1 or 2 will be recoded as 1, and 0 will remain 0.

```{r, eval = FALSE, echo = FALSE}

alldf$Animal<-as.numeric(alldf$Animal)
alldf$ConfAnim<-as.numeric(alldf$ConfAnim)

alldf$ID_unique<-paste(alldf$Site, alldf$Season, alldf$IMG_ID_nospl, sep = "/")

alldf<-alldf %>%
  group_by(ID_unique)%>%
  mutate(SumAnimal = sum(Animal), MeanConf = mean(ConfAnim), MaxConf = max(ConfAnim)) %>% 
  ungroup()
  
alldf$Camera<-dirname(alldf$IMG_ID)


df<-alldf%>%
  dplyr::select(IMG_ID_nospl, ID_unique, Site,Camera ,Season,  SumAnimal, MeanConf)%>%
  distinct() 

df$SumAnimal[df$SumAnimal == 2]<-1

df$SumAnimalF<-as.factor(df$SumAnimal)   #creating a factor for animal presence - for plotting.

cam_split<-strsplit(df$Camera, "/")

get_first<-function(x){
  image_out<-x[[1]]
  return(image_out)
  }

cam_out<-lapply( cam_split,get_first)

df$CamUnique<-unlist(cam_out)


```

```{r, eval = FALSE, echo =FALSE}

camsum<-df %>%
  group_by(CamUnique,SumAnimalF)%>%
  #filter(MeanConf >= 0.9)%>%
  summarise(Freq = n())

#write.csv(camsum, "Camera_Animal_No_Animal.csv", row.names = FALSE)

```

```{r, eval = FALSE, echo = FALSE}

df_tot<-df
df_tot$Site<-"Total"

df_all<-rbind(df, df_tot)
df_all$Site<-as.factor(df_all$Site)

#write.csv(df_all, "Kenya_Animal_No_Animal.csv", row.names = FALSE)
```

```{r, echo = FALSE}

#df_all<-vroom::vroom("Kenya_Animal_No_Animal.csv")

df_all<-df_all %>% 
  filter(Site != "Total")

df_all$Site_f<-as.factor(df_all$Site)
df_all$Site_f<-factor(df_all$Site_f, levels(df_all$Site_f)[c(5,2,4,3,1)])

df_all$SumAnimalF<-as.factor(df_all$SumAnimalF)

site_labs<- c("Total", "Mara North", "Mara Triangle", "Naboisho", "OMC")
names(site_labs)<-c("Total", "mara_north", "mara_triangle", "naboisho", "omc")

loc_spl<-strsplit(df_all$Camera, "_")

loc_splout<-lapply(loc_spl,get_first)
loc_out<-do.call(rbind, loc_splout)


df_all$Location<-as.character(loc_out)

df_all$SiteCode<-df_all$Site
df_all$SiteCode[df_all$SiteCode == "mara_north"]<-"MN"
df_all$SiteCode[df_all$SiteCode == "mara_triangle"]<-"MT"
df_all$SiteCode[df_all$SiteCode == "naboisho"]<-"NB"
df_all$SiteCode[df_all$SiteCode == "omc"]<-"OMC"


df_all$IMG_no<-basename(df_all$IMG_ID_nospl)
df_all$IMG_no<-gsub("IMG_", "",df_all$IMG_no)
df_all$IMG_no<-as.numeric(df_all$IMG_no)



# get_last<-function(x){
#   image_out<-x[[(length(x))]]
#   return(image_out)
# }
# 
# cam_spl<-strsplit(df_all$Camera, "_")
# cam_splout<-lapply(cam_spl,get_last)
# cam_out<-do.call(rbind, cam_splout)

df_all$Camera<-dirname(df_all$IMG_ID_nospl)  #removes everything before the _first_ underscore
df_all$Camera_ID<-basename(df_all$Camera)  #removes everything before the _first_ underscore
df_all$Camera_ID<-gsub("^[^_]*_", "",df_all$Camera_ID)  #removes everything before the _first_ underscore

df_all$ab<-"a"


abs<-which(grepl("101_BTCF",df_all$ID_unique))
df_all$ab[abs]<-"b"
abs<-which(grepl("b",df_all$Camera_ID))
df_all$ab[abs]<-"b"


df_all$IMG_no<-ifelse(df_all$ab == "b", df_all$IMG_no + 10000, df_all$IMG_no)

df_all$IMG_no<-ifelse(df_all$Season == "november", df_all$IMG_no + 20000, df_all$IMG_no)

df_all$IMG_no<-str_pad(df_all$IMG_no,6 , pad = "0")


Sensor<-"CT"
Year<-"2018"

df_all$new_filepath<-paste0("M:/biome_health_project_files/country_files/kenya/working_data/", df_all$SiteCode, "/", df_all$Location, "/", Sensor, "/", Year, "/", Year, "_", df_all$Location, "_",df_all$IMG_no, ".JPG", sep ="")

#write.csv(df_all, "Kenya_Animal_No_Animal_Filepath.csv", row.names = FALSE)

```


You can ignore below here

```{r}

image<-vroom::vroom("kenya_original_filepaths_working_filepaths_2019_10_18.csv",delim = ",")


df_image<-merge(image[,c("IMG_ID_nospl", "new_file_structure")], df_sub, by = "IMG_ID_nospl")



issues<-df_all[!df_all$new_filepath %in% image$new_file_structure,]

issues_i<-image[!image$new_file_structure %in% df_all$new_filepath,]

mn37<-df_all %>% 
  filter(Location == "MN37" & Season == "october")


mn37_i<-issues%>% 
  filter(Location == "MN37" & Season == "october") %>% 
  mutate(IMG_no = as.numeric(IMG_no)) %>% 
  arrange(IMG_no)



```

```{r}

image$IMG_ID_nospl<-image$filepath %>% 
                gsub(".JPG", "", .) %>% 
                gsub("M:/biome_health_project_files/country_files/kenya/raw_data//mara_north_november/", "", .) %>% 
                gsub("M:/biome_health_project_files/country_files/kenya/raw_data//mara_north_october/" ,"", .) %>% 
                gsub("M:/biome_health_project_files/country_files/kenya/raw_data//mara_triangle_november/" ,"", .) %>%                                            gsub("M:/biome_health_project_files/country_files/kenya/raw_data//mara_triangle_october/" ,"", .) %>%                                             gsub("M:/biome_health_project_files/country_files/kenya/raw_data//mara_north_october/" ,"", .) %>% 
                gsub("M:/biome_health_project_files/country_files/kenya/raw_data//naboisho_november_repaired/" ,"", .) %>% 
                gsub("M:/biome_health_project_files/country_files/kenya/raw_data//naboisho_october_repaired/" ,"", .) %>%
                gsub("M:/biome_health_project_files/country_files/kenya/raw_data//omc_october_repaired/" ,"", .) %>% 
                gsub("M:/biome_health_project_files/country_files/kenya/raw_data//omc_november/" ,"", .) 


head(image$ID_unique)

#image<-image %>% 
#            mutate(IMG_ID_nospl = paste(basename(dirname(ID_unique)),basename(ID_unique), sep = "/"))
  
# image<-image %>% 
#             mutate(IMG_ID_nospl = paste(basename(dirname(ID_unique)),basename(ID_unique), sep = "/"))
# 

      
df_sub<-df_all %>% 
  filter(Site != "Total" & Site_f != "Total")


df_image<-merge(image[,c("IMG_ID_nospl", "new_file_structure")], df_sub, by = "IMG_ID_nospl")


not_in<-image[!image$IMG_ID_nospl %in% df_sub$IMG_ID_nospl,]

```

###The rest of the code is just for making various plots of the data


```{r}
ggplot(df_all, aes(SumAnimalF, fill = SumAnimalF))+
  geom_bar()+
  facet_wrap(.~Site_f, labeller = labeller(Site_f = site_labs))+
  labs(x = "", y = "Number of Images")+
  scale_x_discrete(labels=c("0" = "No Animal", "1" = "Animal"))+
  scale_y_continuous(labels = comma)+
  scale_fill_manual( values = c("0" = "black", "1" = "grey"))+ 
  theme_bw()+
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 14),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.position = "none",
        strip.text.x = element_text(size = 14))


```

```{r}

sitesum<-df_all %>%
  group_by(Site_f,SumAnimalF,  SiteCode)%>%
  #filter(MeanConf >= 0.9)%>%
  summarise(Freq = n())

sitesum$SumAnimalF<-as.factor(sitesum$SumAnimalF)
sitesum$SumAnimalF<-factor(sitesum$SumAnimalF, levels(sitesum$SumAnimalF)[c(2,1)])


ggplot(sitesum, aes(x =Site_f ,y = Freq ,alpha = SumAnimalF, fill = Site_f))+
  geom_bar(position="dodge", stat="identity")+
  labs(x = "", y = "Number of Images", fill ="", alpha = "")+
  scale_alpha_discrete(range = c(1, 0.35), labels = c("Animal", "No Animal"))+
  scale_x_discrete(labels=c("mara_north" = "Mara North", "mara_triangle" = "Mara Triangle", "naboisho" = "Naboisho", "omc" = "OMC"))+
  guides(fill = FALSE)+
  scale_y_continuous(labels = comma)+
  theme_bw()+
  #scale_fill_manual(values = c("0" = "black", "1" = "grey"), labels = c("No Animal", "Animal"))+ 
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 18),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text = element_text(size = 18))


#write.csv(sitesum, "Kenya_Animal_No_Animal_Summary.csv", row.names = FALSE)

```

###Image counts with effort accounted for

```{r}
ef<-read.csv("all_sites_effort.csv", stringsAsFactors = FALSE)

ef_sum <-ef %>%
  group_by(site)%>%
  summarise(sum_ef = sum(effort))

ef_tot<-data.frame("Total",sum(ef$effort) )
colnames(ef_tot)<-colnames(ef_sum)

ef_all<-rbind(ef_tot, ef_sum)

```

```{r, echo = FALSE}

site_ef<-merge(ef_all, sitesum, by.x = "site", by.y = "SiteCode")

site_ef$FreqEff<-site_ef$Freq/site_ef$sum_ef


```

```{r}

ggplot(site_ef, aes(x =Site_f ,y = FreqEff ,alpha = SumAnimalF, fill = Site_f))+
  geom_bar(position="dodge", stat="identity")+
  labs(x = "", y = "Number of Images per Camera Trap Day", fill ="", alpha = "")+
  scale_alpha_discrete(range = c(1, 0.35), labels = c("Animal", "No Animal"))+
  scale_x_discrete(labels=c("mara_north" = "Mara North", "mara_triangle" = "Mara Triangle", "naboisho" = "Naboisho", "omc" = "OMC"))+
    scale_y_continuous(labels = comma)+
  guides(fill = FALSE)+
  theme_bw()+
  #scale_fill_manual(values = c("0" = "black", "1" = "grey"), labels = c("No Animal", "Animal"))+ 
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 18),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text = element_text(size = 18))

```


##Excluding images below 90% Confidence Threshold

```{r, echo = FALSE}

sitesum<-df_all %>%
  group_by(Site_f,SumAnimalF,  SiteCode)%>%
  filter(MeanConf >= 0.9)%>%
  summarise(Freq = n())

sitesum$SumAnimalF<-as.factor(sitesum$SumAnimalF)
sitesum$SumAnimalF<-factor(sitesum$SumAnimalF, levels(sitesum$SumAnimalF)[c(2,1)])

site_ef<-merge(ef_all, sitesum, by.x = "site", by.y = "SiteCode")

site_ef$FreqEff<-site_ef$Freq/site_ef$sum_ef

```

####90% Confidence Threshold *not* accounting for effort

```{r, echo = FALSE}
sitesum<-df_all %>%
  group_by(Site_f,SumAnimalF,  SiteCode)%>%
  filter(MeanConf >= 0.9)%>%    ##might wanna change this to MaxConf
  summarise(Freq = n())

sitesum$SumAnimalF<-as.factor(sitesum$SumAnimalF)
sitesum$SumAnimalF<-factor(sitesum$SumAnimalF, levels(sitesum$SumAnimalF)[c(2,1)])


ggplot(sitesum, aes(x =Site_f ,y = Freq ,alpha = SumAnimalF, fill = Site_f))+
  geom_bar(position="dodge", stat="identity")+
  labs(x = "", y = "Number of Images", fill ="", alpha = "")+
  scale_alpha_discrete(range = c(1, 0.35), labels = c("Animal", "No Animal"))+
  scale_x_discrete(labels=c("mara_north" = "Mara North", "mara_triangle" = "Mara Triangle", "naboisho" = "Naboisho", "omc" = "OMC"))+
  scale_y_continuous(labels = comma)+
  guides(fill = FALSE)+
  theme_bw()+
  #scale_fill_manual(values = c("0" = "black", "1" = "grey"), labels = c("No Animal", "Animal"))+ 
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 18),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text = element_text(size = 18))

```

####90% Confidence Threshold accounting for effort

```{r}

ggplot(site_ef, aes(x =Site_f ,y = FreqEff ,alpha = SumAnimalF, fill = Site_f))+
  geom_bar(position="dodge", stat="identity")+
  labs(x = "", y = "Number of Images\n per Camera Trap Day", fill ="", alpha = "")+
  scale_alpha_discrete(range = c(1, 0.35), labels = c("Animal", "No Animal"))+
  scale_x_discrete(labels=c("mara_north" = "Mara North", "mara_triangle" = "Mara Triangle", "naboisho" = "Naboisho", "omc" = "OMC"))+
  scale_y_continuous(labels = comma)+
  guides(fill = FALSE)+
  theme_bw()+
  #scale_fill_manual(values = c("0" = "black", "1" = "grey"), labels = c("No Animal", "Animal"))+ 
  theme(axis.text.y = element_text(lineheight = 0.5 , size = 18),
        axis.text.x = element_text(size = 18),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text = element_text(size = 18))



```

